Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-20 manuscript/manuscript.Rmd
stability subsection, recovering c esc in 1D subsection

We evaluated each of the four control approaches considered -- MSY constant mortality, optimal constant escapement, PPO, and Gaussian process interpolation of the latter -- on each of the four scenarios examined (see Sec. TBD).
Furthermore, we characterized the trade-off between economic output and sustainability faced by constant mortality policies.
This was done by evaluating constant mortality policies with a fraction of the optimal mortality rate (specifically, 80%, 90% and 95%).
All evaluations were based on 100 replicate episodes for each

@@

To assess what is the culprit for the classical strategies' low performance with respect to the DRL-based strategies, we plot the duration of each of the 100 evaluation episodes, for each of the strategies.
We see that early episode ends are a rather likely explanation for the wideness of constant escapement's wide reward distribution.
The constant mortality strategy is also observed to lead to near-extinction events rather often, but in this case the episode lengths tend to be concentrated at higher values relative to the constant escapement case.

@@

@@

>>>>

We evaluated each of the four control approaches considered -- MSY constant mortality, optimal constant escapement, PPO, and Gaussian process interpolation of the latter -- on each of the four scenarios examined (see Sec. TBD).
Furthermore, we characterized the trade-off between economic output and sustainability faced by constant mortality policies.
This was done by evaluating constant mortality policies with a fraction of the optimal mortality rate (specifically, 80%, 90% and 95%).
All evaluations were based on 100 replicate episodes.

@@

To assess what is the culprit for the classical strategies' low performance with respect to the DRL-based strategies, we plot the duration of each of the 100 evaluation episodes of each strategy.
We see that early episode ends are a rather likely explanation for the wideness of constant escapement's wide reward distribution.
The constant mortality strategy is also observed to lead to near-extinction events rather often, but in this case the episode lengths tend to be concentrated at higher values relative to the constant escapement case.

@@

## Recovering constant escapement for a single species

While the optimal control for our single-species model \eqref{eq:may} can not be easily proven to be constant escapement (since the right-hand side of that equation is not concave), from experience we can expect for constant escapement to either be optimal or near-optimal.
We give evidence for this intuition by showing that our DRL method recovers a constant escapement solution when trained.
These results are shown in Fig. TBD.

@@

Our main result in this respect is Fig. **TBD**.
There, we plot the *median episode reward difference* between the two DRL-based methods we considered, and the optimal constant escapement strategy.
This figure shows that, for a wide range of parameter values, DRL-based strategies can have a considerable advantage over an optimized constant escapement policy (the single-species optimal solution).
